---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit the README.Rmd file -->


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Lab report #1

Follow the instructions posted at https://ds202-at-isu.github.io/labs.html for the lab assignment. The work is meant to be finished during the lab time, but you have time until Monday evening to polish things.

Include your answers in this document (Rmd file). Make sure that it knits properly (into the md file). Upload both the Rmd and the md file to your repository.  

All submissions to the github repo will be automatically uploaded for grading once the due date is passed.
Submit a link to your repository on Canvas (only one submission per team) to signal to the instructors that you are done with your submission.

```{r}
library(classdata)
head(ames)
```

The ames data set contains the following variables followed by what we expect the range of each to be:

* parcel id
* Address
* Style
* Occupancy
* Sale Date (1900-2025)
* Sale Price (0-2.5M)
* Multi Sale
* Year Built (1900-2025)
* Acres (0-5)
* Square Feet (0-10,000)
* Bedrooms (0-5)
* Finished Basement SF (0-700)
* Lot Area SF (0-100,000)
* AC (Yes/No)
* Fireplace (Yes/No)
* Neighborhood

2. The variable of special interest or focus is Sale Price.

3. Range of the variable, histogram, and general pattern.


```{r}

range(ames$`Sale Price`, na.rm = TRUE)

```


```{r}
library(ggplot2)
ggplot(ames, aes(x = log(get("Sale Price")))) + 
  geom_histogram(binwidth=2) +
  ggtitle("Sale Price Histogram")


```


Devon's Work:
```{r}
range(ames$YearBuilt, na.rm = TRUE)
```
```{r}
library(dplyr)
library(ggplot2)
year <- filter(ames, YearBuilt != 0 & get("Sale Price")!=0)
ggplot(year, aes(x = YearBuilt)) + 
  geom_histogram(binwidth = 1) +
  ggtitle("Year Built Histogram")
```

After removing an outlier with the value 0, the distribution of Year built seems to increase as the years become more current. There are various peaks and valleys.

```{r}
library(dplyr)
library(ggplot2)
ggplot(year, aes(y = log(get("Sale Price")), x = YearBuilt)) + 
  geom_point() +
  ggtitle("Sale Price Histogram")
```

There does not appear to be a relationship between YearBuilt and Sale Price. The sale prices of homes seems to be relatively constant across years that homes were built.However, this graph shows that some of the lowest sale prices were houses built around the time of the 2008 housing crisis.
