---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit the README.Rmd file -->


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Lab report #1

Follow the instructions posted at https://ds202-at-isu.github.io/labs.html for the lab assignment. The work is meant to be finished during the lab time, but you have time until Monday evening to polish things.

Include your answers in this document (Rmd file). Make sure that it knits properly (into the md file). Upload both the Rmd and the md file to your repository.  

All submissions to the github repo will be automatically uploaded for grading once the due date is passed.
Submit a link to your repository on Canvas (only one submission per team) to signal to the instructors that you are done with your submission.

```{r}
library(classdata)
head(ames)
```

2. The variable of special interest or focus is Sale Price.

3. Range of the variable, histogram, and general pattern.


```{r}

range(ames$`Sale Price`, na.rm = TRUE)

```


```{r}
library(ggplot2)
ggplot(ames, aes(x = log(get("Sale Price")))) + 
  geom_histogram(binwidth=2) +
  ggtitle("Sale Price Histogram")


```

```{r}
range(ames$Bedrooms, na.rm = TRUE)

library(ggplot2)
ggplot(ames, aes(x = Bedrooms, y = log(get("Sale Price")))) +
  geom_point(color = "blue") +
  theme_minimal() +
  labs(title = "Scatter Plot of Bedrooms vs Sale Price",
       x = "Number of Bedrooms",
       y = "Sale Price")

```

Luca: I chose the variable Bedrooms. Bedrooms and Sale Price do not show correlation. The majority of the homes have 2-5 bed rooms and there are some outliers. There is one outlier of 10 bedrooms, but the price is in the normal range.
