---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit the README.Rmd file -->


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Lab report #1

Follow the instructions posted at https://ds202-at-isu.github.io/labs.html for the lab assignment. The work is meant to be finished during the lab time, but you have time until Monday evening to polish things.

Include your answers in this document (Rmd file). Make sure that it knits properly (into the md file). Upload both the Rmd and the md file to your repository.  

All submissions to the github repo will be automatically uploaded for grading once the due date is passed.
Submit a link to your repository on Canvas (only one submission per team) to signal to the instructors that you are done with your submission.

```{r}
library(classdata)
head(ames)
```

2. The variable of special interest or focus is Sale Price.

3. Range of the variable, histogram, and general pattern.


```{r}

saleprice <- range(ames$`Sale Price`, na.rm = TRUE)
saleprice
```


```{r}
library(ggplot2)
ggplot(ames, aes(x = log(get("Sale Price")))) + 
  geom_histogram(binwidth=2) +
  ggtitle("Sale Price Histogram")


```
Most of the sale prices are around the 11-13 range. There are no outliers, and not many homes have a sale price above or below the 11-13 range.




4.
Izzy's Variable: Style
Range:
```{r}

unique(ames$Style)
#since it is categorical, these are the unique values for "Style"

```
Since the style is categorical, the range is a list of the types of styles of houses in Ames.

```{r}
library(ggplot2)
ggplot(ames, aes(Style, log(get("Sale Price")))) +
  scale_x_discrete(guide = guide_axis(n.dodge=3)) +
  geom_boxplot()

```


